\documentclass[12pt,twocolumn]{article}

\begin{document}

\title{Introducing radiant object vectors}

\author{John D.H. Pritchard \thanks{@syntelos, logicalexistentialism@gmail.com}}

\date{\today}

\maketitle

%\tableofcontents

\begin{abstract}

Radiant object theory \cite{ROTI}, topology \cite{ROTY}, applications
\cite{ROTA}, continuity \cite{ROTC}, security \cite{ROTS}, and
integrity \cite{ROTN} opened a perspective on social peer trust
networks.  Radiant object vectors is an evolution of that examination
of distributed objects.  
  
\end{abstract}


\section{Structure}

A unique producer of distributed objects collects production sets
ordered in time.  Likewise, application sets may be collected by a
method of curation, or automated.  Each member of a set is a unique
object or vector, by instance or reference, local or remote.

A vector member reference may include metadata.  Generally, vector
member relations including comparison and order are in member object
metadata.

A producer of radiant objects is a member of a social peer trust
network \cite{ROTI}.  A traditional trust application \cite{ROTA,ROTN}
colors trust as white, distrust as black, and uncertainty as gray.
White listed producers are members of social peer trust networks, and
black listed producers are excluded from social peer trust networks.

\section{Identity}

A vector and object have equivalence of referential identity
\((\kappa)\) and metadata, including the properties and attributes of
production and origin \((\sigma + \iota)\).

$$
  {\kappa} = {\sigma} + {\iota}
$$

\section{Existence}

A vector and object have equivalence of referential existence
\((\epsilon)\).  Any vector or object has referential reachability
\((\rho)\) as well as a referential indeterminancy (\(\nu\)).  A
reference may refer to a set or object that remains to be retrieved,
completed, or updated.

$$
 {\epsilon} =  {\rho} + {\nu}
$$

\section{Continuity}

The membership relation \((\mu\kappa)\) over a vector
\((\epsilon\kappa)\) is partial.

$$
 0 \le \frac{\mu\kappa}{\epsilon\kappa} \le 1
$$

A vector (subset) is continuous when its membership is contiguous and
complete.

\section{Consistency}

Any relation over a vector \((\phi\kappa)\) is partial.

$$
 0 \le \frac{\phi\kappa}{\epsilon\kappa} \le 1
$$

Ideally, the relation \((\phi)\) and object \((\kappa)\) are
enumerable as are the elements of comparison.  An enumerated set is
complete.  A relational specification set agrees with a relational
production set by equivalence of membership to prove consistency by
demonstration.

In practice, however, enumeration is partial.  Continuity is local.
And, consistency is uncertain.

\section{Notes}

In use, consistency has the metaphysical character of the confidence
of good faith.  The conservation of metaphysical confidence demands
the conservation of consistency as continuity.


\break
\appendix

\bibliographystyle{plain}
\bibliography{rov}

\end{document}
