\documentclass[12pt,twocolumn]{article}

\begin{document}

\title{Radiant object vector distribution}

\author{John D.H. Pritchard \thanks{@syntelos, logicalexistentialism@gmail.com}}

\date{\today}

\maketitle

%\tableofcontents

\begin{abstract}

Radiant object theory \cite{ROTI,ROTY,ROTA,ROTC,ROTS,ROTN} opened a
perspective on social peer trust networks.  Radiant object vectors
\cite{ROVI} is an evolution of that examination of distributed
objects.  This effort is a review of that work.
  
\end{abstract}


\section{Structure}

Social peer topology is typically exemplified by {\tt git} \cite{GIT}.
Object reference targets are (functionally equivalent to) persistent
and immutable content (version) hash symbols (like git commit
identifiers).  Collections are software project directory structures.
Distribution is push - pull agnostic.

The radiant object vector is like a collection of {\tt git} projects
in that the radiant object is like a software project directory
structure \cite{ROTI, ROVI}.  In radiant object theory, distribution
is push - pull agnostic.  Like {\tt git}, peer topology is
distributed.  Unlike {\tt git}, radiant object vectors need a fidelity
of immediate continuity for the integrity of local order consistency.

Each endpoint is able to determine logical integrity constraints to
manage the consumer store when application references are object
constrained.  When an object is a software project directory structure
\cite{MIME}, dependencies are constrained to the object like a self
contained HTML or SVG \cite{HTML,SVG}.  Self contained objects are
endpoint managed \cite{DTN,PKG}.  Object vector integrity is regional
\cite{ROVI}.

The general shape of push - pull agnosticism is that interaction is an
endpoint process independent of communication \cite{ROTA}.

$$
 \pi^{\lambda}_S \leftarrow \sum^{\rho\nu}_{\tau\kappa} \pi^{\alpha}_{D}
$$

A trusted peer contact may include an interaction, which may yield a
distributed broadcast occasion according to store and forward
architecture and management.

Unlike {\tt git}, radiant object distribution yields a producer cache
store vector that requires local continuity and consistency.  As a
result, the push - pull distribution event is a synchronization
occasion constrained by vector, store, and forward architecture and
management.  Unlike {\tt git}, rewriting a radiant object produces an
independent object.

\break
\appendix

\bibliographystyle{plain}
\bibliography{rov}

\end{document}
